### 2024-03-15 ms.qmd
Seems like wrong MS, but did some editing

Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth]. These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, that are crucial for the survival and reproduction of animals [@dukas_evolutionary_2004]. Particularly, learning - the acquisition of neuronal representations of new information [@dukas_evolutionary_2004] - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013]. However, in nature, there is individual variation in the capacity to acquire new information, depending on factors like age, sex, gut microbiota, or the environment where organisms develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning]. The latter can be particularly relevant since the brain is especially susceptible to environmental conditions during early stages of development [@zhu_prenatal_2004]. Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.  

@@

Regarding incubation temperature, we predicted hot-incubated lizards to perform better in our task then those incubated at 23ºC, since most of the studies show enhanced learning abilities with higher incubation temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. Furthermore, those studies that found the opposite pattern, were only when the hot treatment was above the natural thermal range of the species [@dayananda_incubation_2017; @abayarathna_effects_2020]. However, our results do not align with these previous experiments and our predictions. In contrast, we did not find any effect of temperature in _L. delicata_ or _L. guichenoti_. In general, the incubation temperature effects observed on learning performance are associated with higher neural density in certain areas [@amiel_effects_2017], but these effects can be region-dependent [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017]. Hence, as ocurred with CORT, further studies using different cognitive domains should be used to understand the effects of incubation temperature on learning abilities in these species.  
Finally, we did not see any significant difference in learning rates when both species were compared. This result is in line with previous studies that found no differences in learning abilities between _L. delicata_ and _L. guichenoti_ [@bezzina2014does]. However, in the experiment conducted by @bezzina2014does the authors did not find any evidence of learning in neither _L. delicata_ or _L. guichenoti_. In this regard, both learning tasks were conducted in a similar way and using the same cognitive domain, so the differences in the results could be due to the different experimental designs or the complexity of stimuli discrimination. Nevertheless, to test cognitive difference between these two species, further studies should be conducted using different cognitive domains.    
In conclusion, we found that neither prenatal CORT, temperature, or their interaction affected learning abilities when _L. delicata_ and _L. guichenoti_ were subjected to a colour-associative task. However, we believe studying different cognitive domains is necessary to understand the effects of early-life stress and incubation temperature on learning abilities in these species. In addition, we found a bias towards blue that could affect the results found in cognitive tests, and we therefore recommend to select carefully the colours employed when employing visual stimuli in these two species, particularly _L. delicata_.

>>>>

Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth]. These cognitive processes underpin animal foraging, mate choice, antipredatory strategies and social behaviours that are crucial for the survival and reproduction [@dukas_evolutionary_2004]. Learning - the acquisition of new information [@dukas_evolutionary_2004] - is fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013]. However, in nature, there is individual variation in the capacity to acquire new information, depending on factors like age, sex, gut microbiota, or the environment where organisms develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning]. The latter can be particularly relevant since the brain is especially susceptible to environmental conditions during early stages of development [@zhu_prenatal_2004]. Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.

@@

Regarding incubation temperature, we predicted hot-incubated lizards to perform better in our task then those incubated at 23ºC, since most of the studies show enhanced learning abilities with higher incubation temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. Furthermore, those studies that found the opposite pattern, were only when the hot treatment was above the natural thermal range of the species [@dayananda_incubation_2017; @abayarathna_effects_2020]. However, our results do not align with these previous experiments and our predictions. In contrast, we did not find any effect of temperature in _L. delicata_ or _L. guichenoti_. In general, the incubation temperature effects observed on learning performance are associated with higher neural density in certain areas [@amiel_effects_2017], but these effects can be region-dependent [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017]. Hence, as ocurred with CORT, further studies using different cognitive domains should be used to understand the effects of incubation temperature on learning abilities in these species.  
Finally, we did not see any significant difference in learning rates when both species were compared. This result is in line with previous studies that found no differences in learning abilities between _L. delicata_ and _L. guichenoti_ [@bezzina2014does]. However, in the experiment conducted by @bezzina2014does the authors did not find any evidence of learning in neither _L. delicata_ or _L. guichenoti_. In this regard, both learning tasks were conducted in a similar way and using the same cognitive domain, so the differences in the results could be due to the different experimental designs or the complexity of stimuli discrimination. Nevertheless, to test cognitive difference between these two species, further studies should be conducted using different cognitive domains.    
In conclusion, we found that neither prenatal CORT, temperature, or their interaction affected learning abilities when _L. delicata_ and _L. guichenoti_ were subjected to a colour-associative task. However, we believe studying different cognitive domains is necessary to understand the effects of early-life stress and incubation temperature on learning abilities in these species. In addition, we found a bias towards blue that could affect the results found in cognitive tests, and we therefore recommend to select carefully the colours employed when employing visual stimuli in these two species, particularly _L. delicata_.
